High Mass Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogeneous Catalysis in Highly Sensitive Microreactors

### 2012-04-18 paper.tex
Added trajectory.png to the paper

Ions enter the source region of the TOF-MS through a series of entry Einzel lenses used for focusing the beam hence minimizing divergence. In the source the beam is pushed into the flight tube by an initial repelling push voltage, $V_p$. The ions are hereafter further accelerated from ground potential to the liner potential, $V_L$. Using this setup the drift velocity of an ion starting exactly from the center of the acceleration region corresponds to an energy of $Ze\left(V_L + V_p/2\right)$ where $Ze$ is the charge of the ion. At the end of the flight tube a reflectron is installed. The reflectron is controlled by voltages $V_{R1}$ and $V_{R2}$. The reflectron has two primary purposes: i) The effective drift length is increased hence increasing the resolution of the TOF-MS. ii) The reflectron works as a focusing lens compensating for any initial velocity dispersion of the ions, i.e. ions with an initial higher velocity will have an increased flight length compared to slower ions. The MCP used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion. According to the manufacturer a resolution $m/\Delta m\gtrsim4000$ of the TOF-MS has been shown.

>>>>

Ions enter the source region of the TOF-MS through a series of entry Einzel lenses used for focusing the beam hence minimizing divergence. In the source the beam is pushed into the flight tube by an initial repelling push voltage, $V_p$. The ions are hereafter further accelerated from ground potential to the liner potential, $V_L$. Using this setup the drift velocity of an ion starting exactly from the center of the acceleration region corresponds to an energy of $Ze\left(V_L + V_p/2\right)$ where $Ze$ is the charge of the ion. At the end of the flight tube a reflectron is installed. The reflectron is controlled by voltages $V_{R1}$ and $V_{R2}$. The reflectron has two primary purposes: i) The effective drift length is increased hence increasing the resolution of the TOF-MS. ii) The reflectron works as a focusing lens (cf. Figure~\ref{fig:trajectory}) compensating for any initial velocity dispersion of the ions, i.e. ions with an initial higher velocity will have an increased flight length compared to slower ions. The MCP used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion. According to the manufacturer a resolution $m/\Delta m\gtrsim4000$ of the TOF-MS has been shown.
\begin{figure}
 \includegraphics[width=16cm]{trajectory.png}%
 \caption{Simulated trajectories of ions with initial position variations in the source region illustrating the focusing effect of the reflectron. Red curve corresponds to ions with an initial position in the center of the source region while blue and green curves illustrate trajectories of ions with non-ideal initial positions displaced 6.3\,mm towards and further away from the repelling plate, respectively. Insert shows the difference between displaced ions and the center positioned ion. The models does not include initial velocity dispersion of the ions.\label{fig:trajectory}}%
\end{figure}
